---
title: "GetPlayerPlayingminutesPosition"
output: html_document
---

```{r}
#Start-off and get a picture of what it looks like
game.id <- c("291172&league=289234", "292573&league=289234", "291170&league=289234", "291183&league=289234",
             "291182&league=289234", "291184&league=289234", "292295&league=289234", "282895&league=282881",
             "289758&league=289234", "292286&league=289234", "292941&league=289234", "292736&league=289234",
             "292735&league=289234")[-c(7,10)]
filenames <- paste0(game.id, ".csv")
commentary.df <- rbind(read.csv(filenames[1]), read.csv(filenames[2]), read.csv(filenames[3]), read.csv(filenames[4]),
      read.csv(filenames[5]), read.csv(filenames[6]), read.csv(filenames[7]), read.csv(filenames[8]),
      read.csv(filenames[9]), read.csv(filenames[10]), read.csv(filenames[11]))
caps.df <- read.csv("names.caps.csv")
```
We notice the commentary data uses full names, eg "Yu Tamura", 
whereas the names.caps data uses a letter for the first name, eg "Y Tamura". 

Therefore, use the player names' last names only. (Cutting down first names won't help because of players such as MG Leitch)

```{r}
#commentary.df clean up as described above
player.names <- as.character(commentary.df$player)
space.pos <- regexpr("[[:space:]]", player.names)
commentary.df$player <- substr(player.names, space.pos+1, nchar(player.names))
head(commentary.df,10)

#caps.df clean up as described above
player.names <- as.character(caps.df$names)
space.pos <- regexpr("[[:space:]]", player.names)
caps.df$names <- substr(player.names, space.pos+1, nchar(player.names))
head(caps.df, 10)
```


All players' minutes start at 80*caps

If you are substituted on the nth minute, you lose n minutes

If you are substituted off the nth miute, you lose 80-n minutes


```{r}
#Setup the dataframes
minutes.df <- data.frame(caps.df[,2], caps.df[,3]*80) # All players' minutes set at 80*caps minutes
commentary.teams <- as.character(commentary.df[,3])
commentary.df <- commentary.df[commentary.teams == "Japan",] #subset commentary.df on Japan
commentary.events <- as.character(commentary.df[,5])
subon.df <- commentary.df[commentary.events == "Substitute on",] #dataframe for sub-on data
suboff.df <- commentary.df[commentary.events == "Player substituted",] #dataframe for sub-off data

minutes.df
head(subon.df, 10)
head(suboff.df, 10)
```

```{r}
#Adjust the minutes by:
#If you are substituted on the nth minute, you lose n minutes
#If you are substituted off the nth miute, you lose 80-n minutes

#Function that uses subon.df to adjust minutes.df
for(i in 1:nrow(subon.df)){
  subon.player <- subon.df$player[i] #player being commentated
  player.row.index <- which(minutes.df[,1] == subon.player) #row index of player being commentated
  minutes.df[player.row.index,2] <- minutes.df[player.row.index,2] - subon.df[i,2] #lose n minutes
}
minutes.df
```

Function that uses subon.df to adjust minutes.df

```{r}
#Function that uses suboff.df to adjust minutes.df
for(i in 1:nrow(suboff.df)){
  suboff.player <- suboff.df$player[i] #player being commentated
  player.row.index <- which(minutes.df[,1] == suboff.player) #row index of player being commentated
  minutes.df[player.row.index,2] <- minutes.df[player.row.index,2] + suboff.df[i,2] - 80 #lose 80-n minutes
}
minutes.df
```

Potential bugs found (those who are have total minutes that are multiples of 80 OR minus minutes):

```{r}
#80 multiple minutes

#Leitch - Captain and 9 starts from 9

#Lomano Lava - referred to as Lemeki by commentators instead
subon.df[subon.df$player == "Lemeki",]
suboff.df[suboff.df$player == "Lemeki",]
#Manually impute Lomano Lava
player.index <- minutes.df[,1] == "Lomano Lava"
minutes.df[player.index,2] <- 164 - 31

#Anisi - referred to as Anise by commentators instead
subon.df[subon.df$player == "Anise",]
suboff.df[suboff.df$player == "Anise",]
#Manually impute Lomano Lava
player.index <- minutes.df[,1] == "Anisi"
minutes.df[player.index,2] <- 91
  
#Fetuani - referred to as Lautami by commentators instead
subon.df[subon.df$player == "Lautami",]
suboff.df[suboff.df$player == "Lautami",]
#Manually impute Lomano Lava
player.index <- minutes.df[,1] == "Fetuani"
minutes.df[player.index,2] <- 42

#Valu - referred to as Ai Valu by commentators instead
subon.df[subon.df$player == "Ai Valu",]
suboff.df[suboff.df$player == "Ai Valu",]
#Manually impute Lomano Lava
player.index <- minutes.df[,1] == "Valu"
minutes.df[player.index,2] <- 77

#Kajikawa - 80 minute lock against Georgia and Wales in 2016

#Minus minutes - more than 2 caps
subon.df[subon.df$player == "Lotoahea",]
suboff.df[suboff.df$player == "Lotoahea",]
#Manually impute Lomano Lava
player.index <- minutes.df[,1] == "Lotoahea"
minutes.df[player.index,2] <- 102

minutes.df
```

Notice the Tanaka + Nagare + Uchida adds up to a perfect 880

```{r}
write.csv(minutes.df, "minutes.csv")
```